Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-04-17 stp/paper_aaai/main.tex
Updated abstract

\pdfinfo{
/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
/Author (Submission 1228)
/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{Submission 1228}
\maketitle
\begin{abstract}
The problem of integrating heterogeneous data sources into an ontology is of high 
relevance in the database field. Several techniques exist to approach this 
problem. Nonetheless, side constraints on the data integration cannot be easily 
integrated with these tools and thus the results may be inconsistent. We 
present a new approach that combines Machine Learning and 
Constraint Programming techniques, by modeling the data integration problem as 
a Steiner Tree Problem in a weighted graph. We show that through this approach 
we can achieve better precision, recall and speed compared to state-of-the-art 
approaches. We provide a comprehensive set of experiments backing our 
findings.
\end{abstract}

>>>>

\pdfinfo{
/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
/Author (Submission 1228)
/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{Submission 1228}
\maketitle
\begin{abstract}
%% REWRITTEN:

The problem of integrating heterogeneous data sources into an ontology is highly relevant in the database field.
Several techniques exist to approach the problem, but side constraints on the data cannot be easily implemented and thus the results may be inconsistent.
In this paper we improve previous work by \citeasnoun{taheriyan2016learning} using Machine Learning (ML) to take into account inconsistencies in the data (unmatchable attributes) and encode the problem as a Steiner Tree, for which we use work by \citeasnoun{deuna2016steiner} in Constraint Programming (CP).
Combining ML and CP achieves state-of-the-art precision, recall and speed, and provides a more flexible framework for variations of the problem.

%% OLD:
%The problem of integrating heterogeneous data sources into an ontology is of high 
%relevance in the database field. Several techniques exist to approach this 
%problem. Nonetheless, side constraints on the data integration cannot be easily 
%integrated with these tools and thus the results may be inconsistent. We 
%present a new approach that combines Machine Learning and 
%Constraint Programming techniques, by modeling the data integration problem as 
%a Steiner Tree Problem in a weighted graph. We show that through this approach 
%we can achieve better precision, recall and speed compared to state-of-the-art 
%approaches. We provide a comprehensive set of experiments backing our 
%findings.
\end{abstract}
